---
author: "Satoshi Kato"
title: "Explore officer package for PowerPoint"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
output:
  html_document:
    fig_caption: yes
    pandoc_args:
      - --from
      - markdown+autolink_bare_uris+tex_math_single_backslash-implicit_figures
    keep_md: no
    toc: yes
  word_document:
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: 3
editor_options: 
  chunk_output_type: inline
---

# Setup

```{r setup, include=FALSE}
knitr::opts_knit$set(progress = TRUE, 
                     verbose  = TRUE, 
                     root.dir = ".")

knitr::opts_chunk$set(collapse = FALSE, 
                      comment = "#>", 
                      message = TRUE, 
                      warning = FALSE, 
                      include = TRUE,
                      echo    = TRUE)

```

```{r install.requirements, eval = FALSE}
install.packages("officer",      dependencies = TRUE)

```

```{r require.packages, message=FALSE}
require(tidyverse)
library(magrittr)

require(officer)
require(flextable)

```

# Just trace

according to 

https://davidgohel.github.io/officer/articles/offcran/powerpoint.html

```{r}
my_pres <- read_pptx("pptx_template/my_template.pptx")
knitr::kable(layout_summary(my_pres))

```

```{r}
my_pres <- read_pptx()
my_pres %>% 
  layout_summary()

```

```{r, eval=FALSE}
my_pres %>% print( target = "pptx_template/officer_default.pptx") 

```


# Add content to a slide

Content must be placed on a slide in a new shape.

`ph_with()` is the unique function you should have to use to add content to a slide. It has 3 arguments, the rpptx object, the object to be printed and the location that define the placeholder where shape will be created.

```{r}
my_pres <- add_slide(x = my_pres, layout = "Title and Content", master = "Office Theme")
my_pres
```

**Note that `ph_with` is to be used instead of functions `ph_with_*` and `ph_with_*_at`**

```{r}
my_pres <- ph_with(my_pres, value = "Hello world", location = ph_location_type(type = "title"))
my_pres <- ph_with(my_pres, value = "A footer", location = ph_location_type(type = "ftr"))
my_pres <- ph_with(my_pres, value = format(Sys.Date()), location = ph_location_type(type = "dt"))
my_pres <- ph_with(my_pres, value = "slide 1", location = ph_location_type(type = "sldNum"))
my_pres <- ph_with(my_pres, value = head(letters), location = ph_location_type(type = "body")) 

```

# Write the PowerPoint file

The (updated) Powerpoint file can be generated using the `print()` function along with the target argument:

```{r}
print(my_pres, target = "./output/010_first_example.pptx") 

```

# Content location

The function `ph_with()` is expecting an argument location that will be used to specify the location of the new shape.

This argument must be an object created from a call to one of the `ph_location*` functions (*placeholder location*). 

```{r}
ph_location_type(type = "body")
```

There are several `ph_location*` functions: 

- `ph_location_type()`
- `ph_location_fullsize()`
- `ph_location_label()`
- `ph_location_left()`
- `ph_location_right()`
- `ph_location_template()`
- `ph_location()`

The following code adds text “Hello world” in a new shape.

That shape will inherit its properties from the placeholder that has type `body`. This is defined in the slide layout used by the slide, i.e. `Title and Content` in our example.

```{r}
text_contents <- c(
    "Hello world", 
    "Bonjour monde", 
    "Blah blah blah"
  )

doc <- read_pptx() %>% 
  add_slide() %>% 
  ph_with(
    value = text_contents, 
    location = ph_location_type(type = "body") ) %>% 
  add_slide() %>% 
  ph_with(
    value = text_contents, 
    location = ph_location_type(type = "title") ) %>% 
  add_slide() %>% 
  ph_with("Hello left", location = ph_location_left() ) %>% 
  ph_with("Hello right", location = ph_location_right() ) 

doc %>% 
  print(target = "./output/010_ph_with_location_type.pptx") 

```

the `Title and Content` slide layout has following placeholder with `type`. 

```{r}
read_pptx() %>% 
  layout_properties (
    layout = "Title and Content",
    master = "Office Theme"
  ) %>% 
  select(-master_name) %>%
  arrange(name, id)

```

## Enumerate place holders

```{r}
layout_properties_all <- 
  read_pptx() %>% 
  layout_properties(master = "Office Theme") %>% 
  arrange(name, id)
  
layout_names <- layout_properties_all %>% 
  pull(name) %>% 
  unique()
  
layout_properties_all %>%
  select(-master_name) #%>% as.matrix()
layout_names


layout_viz <- read_pptx()

i = 1
for (i in seq_len(NROW(layout_names))) {
  
  this_layout <- layout_names[i]
  this_layout_properties <- layout_properties_all %>% 
    filter(name == this_layout)
  
  layout_viz <- layout_viz %>% add_slide(layout = this_layout)
  
  j = 1
  for (j in seq_len(NROW(this_layout_properties))) {
    ph_type  <- this_layout_properties$type[j]
    ph_label <- this_layout_properties$ph_label[j]
    
    content <- sprintf("[type = %s] %s", ph_type, ph_label)
    ph_location <- ph_location_label(ph_label = ph_label)
    
    layout_viz <- layout_viz %>% 
      ph_with(value = content, location = ph_location)
  }
}

layout_viz %>% 
  print(target = "./output/010_layout_with_location_type.pptx") 


```




# Remove slide(s)

When `index` is not specified, **LAST** slide will be removed.

```{r}
doc <- read_pptx()
for(i in 1:5) {
  doc <- doc %>% 
  add_slide() %>% 
  ph_with(
    value = paste("slide", i), 
    location = ph_location_type(type = "title") ) 
}

doc %>% length()
doc <- remove_slide(doc, index = 2)
doc <- remove_slide(doc)
doc %>% print(target = "./output/010_remove_2nd_slide.pptx") 

doc %>% length()

for(i in seq_len(length(doc))) {
  doc <- remove_slide(doc)
}
doc %>% length()


```

