---
author: "Satoshi Kato"
title: "Explore officer package for PowerPoint"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
output:
  html_document:
    fig_caption: yes
    pandoc_args:
      - --from
      - markdown+autolink_bare_uris+tex_math_single_backslash-implicit_figures
    keep_md: no
    toc: yes
  word_document:
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: 3
editor_options: 
  chunk_output_type: inline
---

# Setup

```{r setup, include=FALSE}
knitr::opts_knit$set(progress = TRUE, 
                     verbose  = TRUE, 
                     root.dir = ".")

knitr::opts_chunk$set(collapse = FALSE, 
                      comment = "#>", 
                      message = TRUE, 
                      warning = FALSE, 
                      include = TRUE,
                      echo    = TRUE)

```

```{r install.requirements, eval = FALSE}
install.packages("officer", dependencies = TRUE)

```

```{r require.packages, message=FALSE}
require(tidyverse)
library(magrittr)

require(officer)
require(flextable)

```

# Get started

```{r}
# プレゼンレーションの初期化
my_pres <- read_pptx()

# スライドの追加
my_pres <- add_slide(x = my_pres)

# コンテンツの追加
my_pres <- ph_with(
  x        = my_pres,
  value    = "Hello World",                   # コンテンツの指定（図表・テキスト等）
  location = ph_location_type(type = "body")  # コンテンツの設置先の指定
) 

# プレゼンレーションの出力
print(my_pres, target = "output/010_HelloWorld.pptx")

# _is_the_same_as_S3_
# officer:::print.rpptx(
#   x      = my_pres,
#   target = "output/010_HelloWorld.pptx"
# ) 

```

## pipe chain 

```{r}
read_pptx() %>%                                # プレゼンレーションの初期化
  add_slide() %>%                              # スライドの追加
  ph_with(                                     # コンテンツの追加
    value    = "Hello World",                  # - コンテンツの指定（図表・テキスト等）
    location = ph_location_type(type = "body") # - コンテンツの設置先の指定
  ) %>% 
  print(target = "output/010_HelloWorld.pptx") # プレゼンレーションの出力


```

## With customized theme (Master) 

```{r}
read_pptx(path = "./pptx_template/my_template.pptx") %>%  # プレゼンレーションの初期化
  add_slide(                                              # スライドの追加
    master = "my_theme",                                  # - スライドマスターの指定
    layout = "my_custom"                                  # - スライドレイアウトの指定
  ) %>% 
ph_with(                                                  # コンテンツの追加
    value    = "Hello World",                             # - コンテンツの指定（図表・テキスト等）
    location = ph_location_type(type = "body")            # - コンテンツの設置先の指定
  ) %>% 
  print(target = "output/010_HW_with_template.pptx")      # プレゼンレーションの出力


```


# Just trace utilities

according to help and

https://davidgohel.github.io/officer/articles/offcran/powerpoint.html

## master layouts and slide layouts

`read_pptx()` uses a PowerPoint file as the initial document. This is the original PowerPoint document where all slide layouts, placeholders for shapes and styles come from. Major points to be aware of are:

- Slide layouts are relative to a master layout. A document can contain one or more master layouts; a master layout can contain one or more slide layouts.
- A slide layout inherits design properties from its master layout but some properties can be overwritten.
- Designs and formatting properties of layouts and shapes (placeholders in a layout) are defined within the initial document. There is no R function to modify these values - they must be defined in the initial document.


```{r}
my_pres <- read_pptx("pptx_template/my_template.pptx")
knitr::kable(layout_summary(my_pres))

```

<<<<<<< HEAD
```{r}
my_pres <- read_pptx()
my_pres %>% 
  layout_properties (
    master = "Office Theme",      # スライドマスターの指定
    layout = "Title and Content"  # スライドレイアウトの指定
  ) %>% 
  mutate_if(is.numeric, ~round(., digits = 3))
```

```{r}
annotate_base(
  path = NULL,                                     # レイアウトを確認したいPPTXファイル
  output_file = "output/010_annotated_layout.pptx" # 出力先 
)

```
=======
>>>>>>> a2949a1224ac0d71f10e9164d46752542bdb2892

# Add content to a slide

Content must be placed on a slide in a new shape.

`ph_with()` is the unique function you should have to use to add content to a slide. It has 3 arguments, the rpptx object, the object to be printed and the location that define the placeholder where shape will be created.

```{r}
my_pres <- add_slide(
  x      = my_pres,             # スライドを追加したいプレゼンテーションの指定
  layout = "Title and Content", # 追加したいスライドのレイアウトの指定
  master = "Office Theme"       # 追加したいレイアウトを持っているマスターの指定
)
my_pres
```

```{r}
ph_location_type(ph_label = ph_label)
```


```

**Note that `ph_with` is to be used instead of functions `ph_with_*` and `ph_with_*_at`**

```{r}
my_pres <- ph_with(my_pres, value = "Hello world", location = ph_location_type(type = "title"))
my_pres <- ph_with(my_pres, value = "A footer", location = ph_location_type(type = "ftr"))
my_pres <- ph_with(my_pres, value = format(Sys.Date()), location = ph_location_type(type = "dt"))
my_pres <- ph_with(my_pres, value = "slide 1", location = ph_location_type(type = "sldNum"))
my_pres <- ph_with(my_pres, value = head(letters), location = ph_location_type(type = "body")) 

```

# Write the PowerPoint file

The (updated) Powerpoint file can be generated using the `print()` function along with the target argument:

```{r}
print(my_pres, target = "./output/010_first_example.pptx") 

```

# Content location

The function `ph_with()` is expecting an argument location that will be used to specify the location of the new shape.

This argument must be an object created from a call to one of the `ph_location*` functions (*placeholder location*). 

```{r}
ph_location_type(type = "body")
```

There are several `ph_location*` functions: 

- `ph_location_type()`
- `ph_location_fullsize()`
- `ph_location_label()`
- `ph_location_left()`
- `ph_location_right()`
- `ph_location_template()`
- `ph_location()`

The following code adds text “Hello world” in a new shape.

That shape will inherit its properties from the placeholder that has type `body`. This is defined in the slide layout used by the slide, i.e. `Title and Content` in our example.


## location by placeholder type

placeholder type to look for in the slide layout, one of 'body', 'title', 'ctrTitle', 'subTitle', 'dt', 'ftr', 'sldNum'.

the `Title and Content` slide layout has following placeholder with `type`. 

```{r}
read_pptx() %>% 
  layout_properties (
    layout = "Title and Content",
    master = "Office Theme"
  ) %>% 
  select(-master_name) %>%
  arrange(name, id)

```

```{r}
text_contents <- c(
    "Hello world", 
    "Bonjour monde", 
    "Blah blah blah"
  )

doc <- read_pptx() %>% 
  add_slide() %>% 
  ph_with(
    value = text_contents, 
    location = ph_location_type(type = "body") ) %>% 
  add_slide() %>% 
  ph_with(
    value = text_contents, 
    location = ph_location_type(type = "title") ) %>% 
  add_slide() %>% 
  ph_with("Hello left", location = ph_location_left() ) %>% 
  ph_with("Hello right", location = ph_location_right() ) 

doc %>% 
  print(target = "./output/010_ph_with_location_type.pptx") 

```

<<<<<<< HEAD


=======
the `Title and Content` slide layout has following placeholder with `type`. 

```{r}
read_pptx() %>% 
  layout_properties (
    layout = "Title and Content",
    master = "Office Theme"
  ) %>% 
  select(-master_name) %>%
  arrange(name, id)

```
>>>>>>> a2949a1224ac0d71f10e9164d46752542bdb2892

# Remove slide(s)

When `index` is not specified, **LAST** slide will be removed.

```{r}
doc <- read_pptx()
for(i in 1:5) {
  doc <- doc %>% 
  add_slide() %>% 
  ph_with(
    value = paste("slide", i), 
    location = ph_location_type(type = "title") ) 
}

doc %>% length()
doc <- remove_slide(doc, index = 2)
doc <- remove_slide(doc)
doc %>% print(target = "./output/010_remove_2nd_slide.pptx") 

doc %>% length()

for(i in seq_len(length(doc))) {
  doc <- remove_slide(doc)
}
doc %>% length()


```

