---
author: "Satoshi Kato"
title: "Explore officer package for PowerPoint"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
output:
  html_document:
    fig_caption: yes
    pandoc_args:
      - --from
      - markdown+autolink_bare_uris+tex_math_single_backslash-implicit_figures
    keep_md: no
    toc: yes
  word_document:
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: 3
editor_options: 
  chunk_output_type: inline
---

# Setup

```{r setup, include=FALSE}
knitr::opts_knit$set(progress = TRUE, 
                     verbose  = TRUE, 
                     root.dir = ".")

knitr::opts_chunk$set(collapse = FALSE, 
                      comment = "#>", 
                      message = TRUE, 
                      warning = FALSE, 
                      include = TRUE,
                      echo    = TRUE)

```

```{r install.requirements, eval = FALSE}
install.packages("officer",      dependencies = TRUE)

```

```{r require.packages, message=FALSE}
require(tidyverse)
library(magrittr)

require(officer)
require(flextable)

```

# Just trace (Continued)

according to 

https://davidgohel.github.io/officer/articles/offcran/powerpoint.html


```{r}
my_pres <- read_pptx()
my_pres %>% 
  layout_summary() %>% 
  knitr::kable()

```


# Supported contents and layouts

The following types of content are supported:

- `vectors` of `text`, `numeric` and `factor`
- `block_list`, `unordered_list` when formatting is complex
- `data.frame`
- `ggplot` objects
- `external_img`
- `flextable::flextable`
- `rvg::dml`


## Text and vectors


```{r}
doc <- read_pptx()

doc <- doc %>% 
<<<<<<< HEAD
  add_slide() %>% 
  ph_with(value = pi,
          location = ph_location_type(type = "title") ) %>% 
  ph_with(value = c("箇条書きの１", "箇条書きの２"), 
          location = ph_location_type(type = "body") )


```

=======
  add_slide(layout = "Two Content", master = "Office Theme") %>% 
  ph_with(value = pi, 
          location = ph_location_type(type = "title") ) %>% 
  ph_with(value = as.factor(letters[1:2]),
          location = ph_location_type(type = "ftr") ) %>% 
  ph_with(value = c("one blah", "two blah"), 
          location = ph_location_left() ) %>% 
  ph_with(value = c("three blah", "four blah"), 
          location = ph_location_right() ) 

```


>>>>>>> a2949a1224ac0d71f10e9164d46752542bdb2892
## data.frame

```{r}
doc <- doc %>%
  add_slide() %>% 
  ph_with(value = head(iris), 
          location = ph_location_type(type = "body") )

```


<<<<<<< HEAD

# Editable table (flextable)

```{r}
library(flextable)
ft <- iris %>% 
  head() %>% 
  flextable() %>% 
  autofit()

doc <- doc %>% 
  add_slide() %>% 
  ph_with(value = ft,
          location = ph_location_type(type = "body") )

```

=======
>>>>>>> a2949a1224ac0d71f10e9164d46752542bdb2892
## ggplot objects

```{r}
library(ggplot2)
gg_plot <- ggplot(data = iris ) +
  geom_point(
    mapping = aes(Sepal.Length, Petal.Length, color = Species),
    size = 3) + theme_minimal()

```

```{r}
doc <- doc %>% 
  add_slide() %>% 
  ph_with(value = gg_plot,
<<<<<<< HEAD
          location = ph_location_type(type = "body") ) %>% 
=======
          location = ph_location_fullsize() ) %>% 
>>>>>>> a2949a1224ac0d71f10e9164d46752542bdb2892
  ph_with(value = "a ggplot example", 
          location = ph_location_type(type = "title") )

```

<<<<<<< HEAD
### fullsize 

```{r}
doc <- doc %>% 
  add_slide() %>% 
  ph_with(value = gg_plot,
          location = ph_location_fullsize() ) %>% 
  ph_with(value = "a ggplot example (fullsize)", 
          location = ph_location_type(type = "title") )

```

# Editable graphics
=======
# Image files

```{r}
img.file <- file.path( R.home("doc"), "html", "logo.jpg" )

doc <- doc %>% 
  add_slide() %>% 
  ph_with(value = external_img(img.file, width = 1.39, height = 1.06),
          location = ph_location_type(type = "body"), 
          use_loc_size = FALSE)

```


# Editable table (flextable)

```{r}
library(flextable)
ft <- flextable(head(iris))
ft <- autofit(ft)

ft
```

```{r}
doc <- doc %>% 
  add_slide() %>% 
  ph_with(value = ft,
          location = ph_location_type(type = "body") )

```

# Editable graphics (`dml {rvg}`)
>>>>>>> a2949a1224ac0d71f10e9164d46752542bdb2892

- `{rvg}`
  - package for "R Graphics Devices for Vector Graphics Output"
- `dml()`
  - Wrap plot instructions for DrawingML plotting in Powerpoint

A simple wrapper to mark the plot instructions as Vector Graphics instructions. It produces an object of class `dml` with a corresponding method `ph_with`.

The function enable usage of any R plot with argument code and with ggplot objects with argument ggobj.


```{r}
library(rvg)
editable_graph <- rvg::dml(ggobj = gg_plot)

# editable_graph

```

```{r}
<<<<<<< HEAD
library(rvg)

doc <- doc %>% 
  add_slide() %>% 
  ph_with(value    = rvg::dml(ggobj = gg_plot),
=======
doc <- doc %>% 
  add_slide() %>% 
  ph_with(value = editable_graph,
>>>>>>> a2949a1224ac0d71f10e9164d46752542bdb2892
          location = ph_location_type(type = "body") )

```


<<<<<<< HEAD
# Image files

```{r}
img.file <- file.path( R.home("doc"), "html", "logo.jpg" )

doc <- doc %>% 
  add_slide() %>% 
  ph_with(value = external_img(img.file, width = 4, height = 4),
          location = ph_location_type(type = "body"), 
          use_loc_size = FALSE)

```


# Multiple paragraphs with block_list

```{r}
bold_red     <- ftext(
  text = "This is BOLD text", 
  prop = fp_text(
    bold = TRUE, 
    color = "red",
    font.size = 30)
)

italic_ul <- ftext(
  text = "This is Italic text", 
  prop = fp_text(
    italic = TRUE, 
    underlined = TRUE,
    font.family = "Times New Roman", 
    font.size = 48)
)

bl <- block_list(
  fpar(bold_red),
  fpar(italic_ul)
)

doc <- doc %>% 
  add_slide() %>% 
  ph_with(value = bl,
          location = ph_location_type(type = "body") )

```

=======
# Editable table & graph

```{r}
doc <- doc %>% 
  add_slide(layout = "Two Content", master = "Office Theme") %>% 
  ph_with(value = "Editable table & graph", 
          location = ph_location_type(type = "title") ) %>% 
  ph_with(value = ft, 
          location = ph_location_left() ) %>% 
  ph_with(value = editable_graph,
          location = ph_location_right() ) 

```

```{r}
doc <- doc %>% 
  add_slide(layout = "Title and Content", master = "Office Theme") %>% 
  ph_with(value = "Editable table & graph", 
          location = ph_location_type(type = "title") ) %>% 
  ph_with(value = editable_graph, 
          location = ph_location_type(type = "body") ) %>% 
  ph_with(value = c("This RVG is from", 
                    "iris data"),
          location = ph_location_type(type = "body") )

```

# Multiple paragraphs with customized location

```{r}
# first define a block_list made of fpar ----
bl <- block_list(
  fpar(ftext("This is from iris", fp_text(bold = TRUE))),
  fpar(
    ftext("This is from ", fp_text(bold = TRUE, font.size = 30)),
    ftext("iris", prop = fp_text(color = "red", bold = TRUE, font.size = 30) )
  )
)

title_bl <- fpar(
    ftext("Vector Graphics Output & Customized paragraph by officer",
          fp_text(font.size = 24))
  )

```


```{r}
doc <- doc %>% 
  add_slide() %>% 
  ph_with(value = bl, 
          location = ph_location(label = "my_name",
                                 left = 2, top = 3, width = 4, height = 4, 
                                 bg = "wheat", rotation = 90) 
  )

```

```{r}

doc <- doc %>% 
  add_slide() %>% 
  ph_with(value = title_bl, 
          location = ph_location_type(type = "title") ) %>% 
  ph_with(value = editable_graph, 
        location = ph_location_type(type = "body") ) %>% 
  ph_with(value = bl, 
          location = ph_location_type(type = "body") )

```


```{r}
doc <- doc %>% 
  add_slide() %>% 
  ph_with(value = title_bl, 
          location = ph_location_type(type = "title") ) %>% 
  ph_with(value = editable_graph, 
          location = ph_location_type(type = "body") ) %>% 
  ph_with(value = bl, 
          location = ph_location(label = "my_name",
                                 left = 1.5, top = 3, width = 3, height = 0, 
                                 bg = "wheat", rotation = 30) 
  )

```


```{r}
# first define a block_list made of fpar ----
bl <- block_list(
  fpar(ftext("Two Content + Free Object",
             fp_text(bold = TRUE))),
  fpar(
    ftext("This is from ", fp_text(italic  = TRUE, 
                                   font.family = "Times New Roman",
                                   font.size = 30)),
    ftext("iris", prop = fp_text(color = "red", bold = TRUE, font.size = 30) )
  )
)

title_bl <- fpar(
    ftext("Vector Output & Customized paragraph by officer",
          fp_text(font.size = 24))
  )

```


```{r}
doc <- doc %>% 
  add_slide(layout = "Two Content", master = "Office Theme") %>% 
  ph_with(value = title_bl, 
          location = ph_location_type(type = "title") ) %>% 
  ph_with(value = ft, 
          location = ph_location_left() ) %>% 
  ph_with(value = editable_graph,
          location = ph_location_right() ) %>% 
  ph_with(value = bl, 
          location = ph_location(label = "my_name",
                                 left = 1, top = 6, width = 3, height = 0, 
                                 bg = "wheat", rotation = 30) )

```


>>>>>>> a2949a1224ac0d71f10e9164d46752542bdb2892
# write_pptx

```{r}
doc %>% 
<<<<<<< HEAD
  print(target = "./output/020_supportedContents.pptx")

doc
```


=======
  print(target = "./output/020_supportedContents_with_layouts.pptx")

doc
```
>>>>>>> a2949a1224ac0d71f10e9164d46752542bdb2892
