---
author: "Satoshi Kato"
title: "Explore officer package for PowerPoint"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
output:
  html_document:
    fig_caption: yes
    pandoc_args:
      - --from
      - markdown+autolink_bare_uris+tex_math_single_backslash-implicit_figures
    keep_md: no
    toc: yes
  word_document:
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: 3
editor_options: 
  chunk_output_type: inline
---

# Setup

```{r setup, include=FALSE}
knitr::opts_knit$set(progress = TRUE, 
                     verbose  = TRUE, 
                     root.dir = ".")

knitr::opts_chunk$set(collapse = FALSE, 
                      comment = "#>", 
                      message = TRUE, 
                      warning = FALSE, 
                      include = TRUE,
                      echo    = TRUE)

```

```{r install.requirements, eval = FALSE}
install.packages("officer",      dependencies = TRUE)

```

```{r require.packages, message=FALSE}
require(tidyverse)
library(magrittr)

require(officer)
require(flextable)

```

# Just trace (Continued)

according to 

https://davidgohel.github.io/officer/articles/offcran/powerpoint.html


```{r}
my_pres <- read_pptx()
my_pres %>% 
  layout_summary() %>% 
  knitr::kable()

```


# Supported contents and layouts

The following types of content are supported:

- `vectors` of `text`, `numeric` and `factor`
- `block_list`, `unordered_list` when formatting is complex
- `data.frame`
- `ggplot` objects
- `external_img`
- `flextable::flextable`
- `rvg::dml`


## Text and vectors


```{r}
doc <- read_pptx()

doc <- doc %>% 
  add_slide() %>% 
  ph_with(value = pi,
          location = ph_location_type(type = "title") ) %>% 
  ph_with(value = c("箇条書きの１", "箇条書きの２"), 
          location = ph_location_type(type = "body") )


```

## data.frame

```{r}
doc <- doc %>%
  add_slide() %>% 
  ph_with(value = head(iris), 
          location = ph_location_type(type = "body") )

```



# Editable table (flextable)

```{r}
library(flextable)
ft <- iris %>% 
  head() %>% 
  flextable() %>% 
  autofit()

doc <- doc %>% 
  add_slide() %>% 
  ph_with(value = ft,
          location = ph_location_type(type = "body") )

```

## ggplot objects

```{r}
library(ggplot2)
gg_plot <- ggplot(data = iris ) +
  geom_point(
    mapping = aes(Sepal.Length, Petal.Length, color = Species),
    size = 3) + theme_minimal()

```

```{r}
doc <- doc %>% 
  add_slide() %>% 
  ph_with(value = gg_plot,
          location = ph_location_type(type = "body") ) %>% 
  ph_with(value = "a ggplot example", 
          location = ph_location_type(type = "title") )

```

### fullsize 

```{r}
doc <- doc %>% 
  add_slide() %>% 
  ph_with(value = gg_plot,
          location = ph_location_fullsize() ) %>% 
  ph_with(value = "a ggplot example (fullsize)", 
          location = ph_location_type(type = "title") )

```

# Editable graphics

- `{rvg}`
  - package for "R Graphics Devices for Vector Graphics Output"
- `dml()`
  - Wrap plot instructions for DrawingML plotting in Powerpoint

A simple wrapper to mark the plot instructions as Vector Graphics instructions. It produces an object of class `dml` with a corresponding method `ph_with`.

The function enable usage of any R plot with argument code and with ggplot objects with argument ggobj.


```{r}
library(rvg)
editable_graph <- rvg::dml(ggobj = gg_plot)

# editable_graph

```

```{r}
library(rvg)

doc <- doc %>% 
  add_slide() %>% 
  ph_with(value    = rvg::dml(ggobj = gg_plot),
          location = ph_location_type(type = "body") )

```


# Image files

```{r}
img.file <- file.path( R.home("doc"), "html", "logo.jpg" )

doc <- doc %>% 
  add_slide() %>% 
  ph_with(value = external_img(img.file, width = 4, height = 4),
          location = ph_location_type(type = "body"), 
          use_loc_size = FALSE)

```


# Multiple paragraphs with block_list

```{r}
bold_red     <- ftext(
  text = "This is BOLD text", 
  prop = fp_text(
    bold = TRUE, 
    color = "red",
    font.size = 30)
)

italic_ul <- ftext(
  text = "This is Italic text", 
  prop = fp_text(
    italic = TRUE, 
    underlined = TRUE,
    font.family = "Times New Roman", 
    font.size = 48)
)

bl <- block_list(
  fpar(bold_red),
  fpar(italic_ul)
)

doc <- doc %>% 
  add_slide() %>% 
  ph_with(value = bl,
          location = ph_location_type(type = "body") )

```

# write_pptx

```{r}
doc %>% 
  print(target = "./output/020_supportedContents.pptx")

doc
```


