---
author: "Satoshi Kato"
title: "placeholder location and slide layout"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
output:
  html_document:
    fig_caption: yes
    pandoc_args:
      - --from
      - markdown+autolink_bare_uris+tex_math_single_backslash-implicit_figures
    keep_md: no
    toc: yes
  word_document:
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: 3
editor_options: 
  chunk_output_type: inline
---

# Setup

```{r setup, include=FALSE}
knitr::opts_knit$set(progress = TRUE, 
                     verbose  = TRUE, 
                     root.dir = ".")

knitr::opts_chunk$set(collapse = FALSE, 
                      comment = "#>", 
                      message = TRUE, 
                      warning = FALSE, 
                      include = TRUE,
                      echo    = TRUE)

```

```{r install.requirements, eval = FALSE}
install.packages("officer", dependencies = TRUE)

```

```{r require.packages, message=FALSE}
require(tidyverse)
library(magrittr)

require(officer)
require(flextable)

```

# Content location

The function `ph_with()` is expecting an argument location that will be used to specify the location of the new shape.

This argument must be an object created from a call to one of the `ph_location*` functions (*placeholder location*). 

```{r}
ph_location_type(type = "body")
```

There are several `ph_location*` functions: 

- `ph_location_type()`
- `ph_location_label()`
- `ph_location_fullsize()`
- `ph_location_left()`
- `ph_location_right()`
- `ph_location()`

The following code adds text “Hello world” in a new shape.

That shape will inherit its properties from the placeholder that has type `body`. This is defined in the slide layout used by the slide, i.e. `Title and Content` in our example.


## location by type

the `Title and Content` slide layout has following placeholder with `type`. 

```{r}
my_pres <- read_pptx()

```

```{r}
my_pres %>% 
  layout_properties (
    layout = "Title and Content",
    master = "Office Theme"
  ) %>% 
  select(master_name:ph_label)

```

placeholder type to look for in the slide layout, one of 'body', 'title', 'ctrTitle', 'subTitle', 'dt', 'ftr', 'sldNum'.

```{r}
my_pres <- my_pres %>%
  add_slide(
    layout = "Title and Content", master = "Office Theme"
  ) %>% 
  ph_with(                                     # プレースホルダをtypeで指定してコンテンツを設置
    value    = "メインコンテンツ by type", 
    location = ph_location_type(type = "body")
  ) %>% 
  ph_with(                                     # 次のプレースホルダにコンテンツを設置
    value    = "タイトル", 
    location = ph_location_type(type = "title")
  ) %>% 
  ph_with(                                     # 次のプレースホルダにコンテンツを設置
    value    = "日付", 
    location = ph_location_type(type = "dt")
  ) %>% 
  ph_with(                                     # 次のプレースホルダにコンテンツを設置
    value    = "フッター",
    location = ph_location_type(type = "ftr")
  ) %>% 
  ph_with(                                     # 次のプレースホルダにコンテンツを設置
    value    = "スライド番号", 
    location = ph_location_type(type = "sldNum")
  )
  

```

## location by label-name of placeholder

the `Title and Content` slide layout has following placeholder with `ph_label`. 

```{r}
my_pres %>% 
  layout_properties (
    layout = "Title and Content",
    master = "Office Theme"
  ) %>% 
  select(master_name:ph_label)

```

```{r}
my_pres <- my_pres %>%
  add_slide(layout = "Title and Content", master = "Office Theme") %>% 
  ph_with(
    value = "placeholder location by label", 
    location = ph_location_label(ph_label = "Content Placeholder 2")
  )

```

## customized location

`ph_location_left()` and `ph_location_right()` set a content to left and right body-placeholder on slide with "Two Content" layout.

### Two Content

ph_id of officer are diffrent from placeholder index on PPTX-layer

```{r}
my_pres %>% 
  layout_properties (
    layout = "Two Content",
    master = "Office Theme"
  ) %>% 
  select(master_name:ph_label)

```

```{r}

my_pres <- my_pres %>% 
  add_slide(
    layout = "Two Content",        # 左右コンテンツのレイアウト・スライドを追加
    master = "Office Theme"
  ) %>% 
  ph_with(
    value    = c("左 1", "左 2"), 
    location = ph_location_left()  # 左側のプレースホルダにコンテンツを設置
  ) %>% 
  ph_with(
    value    = c("右 1", "右 2"), 
    location = ph_location_right() # 右側のプレースホルダにコンテンツを設置
  ) 

```

### Fullsize Content

`ph_location_fullsize()` expands contents size to fulfilled on current slide.

```{r}
library(ggplot2)
gg_plot <- iris %>% 
  ggplot(aes(Sepal.Length, Petal.Length, color = Species)) +
  geom_point(size = 3)

```

```{r}
my_pres <- my_pres %>% 
  add_slide() %>% 
  ph_with(
    value    = gg_plot, 
    location = ph_location_fullsize()  # スライド全体サイズまでコンテンツを拡大 
  )

```

### customized location

`ph_location()` set a NEW placeholder on current slide.

```{r}
my_pres <- my_pres %>% 
  add_slide(layout = "Title and Content", master = "Office Theme") %>% 
  ph_with(
    value = "Add New Placeholder", 
    location = ph_location(
      newlabel = "new_ph",    # 新しく設置するプレースホルダの名称（再利用のため）
      left = 3, top = 2,      # プレースホルダの位置（左上隅の座標）
      width = 5, height = 2,  # プレースホルダのサイズ
      bg = "wheat",           # プレースホルダの背景色
      rotation = 15           # プレースホルダの回転角
    ) 
  )

```


### customized style and location

```{r}
body_bl <- block_list(
  fpar(
    ftext(text = "example of multi-paragraph",
          prop = fp_text(underlined = TRUE))
    ),
  fpar(
    ftext(text = "Hello ",
          prop = fp_text(italic  = TRUE, font.size = 48,
                         font.family = "Times New Roman")),
    ftext(text = "World",
          prop = fp_text(color = "red", bold = TRUE) ))
)

title_bl <- fpar(
    ftext(text = "Title + Body + Free Object",
          prop = fp_text(color = "green", font.size = 18))
  )

my_pres <- my_pres %>% 
  add_slide(
    layout = "Title and Content",
    master = "Office Theme"
  ) %>% 
  ph_with(
    value = title_bl, 
    location = ph_location(
      left = 4, top = 1, width = 5, height = 0.5, bg = "wheat") 
  ) %>% 
  ph_with(
    value    = body_bl, 
    location = ph_location_type("body")
  ) %>% 
  ph_with(
    value = gg_plot, 
    location = ph_location(
      left = 3, top = 3, width = 4.8, height = 3.6, rotation = 15)
  )

```


# write_pptx

```{r}
my_pres %>% 
  print(target = "./output/030_phLocation_and_layouts.pptx")

my_pres
```

# Remove slide(s)

When `index` is not specified, **LAST** slide will be removed.

```{r}
my_pres <- read_pptx()
for(i in 1:5) {
  my_pres <- my_pres %>% 
  add_slide() %>% 
  ph_with(
    value = paste("slide", i), 
    location = ph_location_type(type = "title") ) 
}

my_pres %>% length()
my_pres <- remove_slide(my_pres, index = 2)
my_pres <- remove_slide(my_pres)
my_pres %>% print(target = "./output/010_remove_2nd_slide.pptx") 

my_pres %>% length()

for(i in seq_len(length(my_pres))) {
  my_pres <- remove_slide(my_pres)
}
my_pres %>% length()


```

